Quality Criteria for SKOS Vocabularies

### 2012-03-20 background.tex
minor consistency fixes in secs 1-3

\section{Background}

@@

SKOS is a language for defining vocabularies in the Web of Data and therefore based on the Open World Assumption. Established quality notions from closed-world systems, such as referential integrity or schema validation, don't hold anymore, because the available information may be incomplete and facts that are not explicitly stated cannot be determined as true or false. While trust and provenance models for Web data are being developed~\cite{Omitola2011,Hartig2009}, content-based and hand-crafted heuristics are currently used to evaluate quality in Linked Data sets~\cite{Heath2011}. Gueret et al. [\todo{CM}{find the right reference in google scholar}], for instance, calculate network measures to support human judgement on the quality of Linked Data \todo{CM}{?} graphs.

@@

% Argue why we need to formalize them -> because otherwise they will be implemented inconsistently across applications
Thus, in order to help vocabulary and application designers in judging the quality of SKOS vocabularies, we need higher-level quality criteria that go beyond low-level integrity conditions, which define data model consistency. Such quality criteria are already well-established and have extensively been discussed in standardized guidelines [\todo{CM}{ISO refs}], manuals [\todo{CM}{hedden book, skosify ref 3}], and scholarly articles [\todo{cm}{e.g., skosify refs 16/17}].
% TODO: bitte hier einfach nur die referenzen auf die wir uns beziehen zusammenfassen und kategorisieren. Schau dir dazu auch nochmals die SKOSify referenzen und die aus eurem iSemantics paper an.
If we want to apply these criteria on SKOS vocabularies, we first need to identify them and determine how to evaluate them given the syntax, structure and semantics of SKOS. Since we want to provide tool support for quality checking, we must formalize these criteria into computable metrics, in order to ensure consistent implementation and interpretation across tools.

>>>>

\section{Background}\label{sec:background}

@@

SKOS is a language for defining vocabularies in the Web of Data and therefore based on the Open World Assumption. Established quality notions from closed-world systems, such as referential integrity or schema validation, don't hold anymore, because available information may be incomplete and non-explicitly stated facts cannot be determined as true or false. While trust and provenance models for Web data are being developed~\cite{Omitola2011,Hartig2009}, content-based and hand-crafted heuristics are currently used to evaluate quality in Linked Data sets~\cite{Heath2011}.

% MOVE TO RELATED WORK: Gueret et al. [\todo{CM}{find the right reference in google scholar}], for instance, calculate network measures to support human judgement on the quality of Linked Data \todo{CM}{?} graphs.

@@

% Argue why we need to formalize them -> because otherwise they will be implemented inconsistently across applications
Thus, in order to help vocabulary and application designers in judging the quality of SKOS vocabularies, we need higher-level quality criteria that go beyond low-level integrity conditions defining data model consistency. Such quality criteria are already well-established and have extensively been discussed in standardized guidelines [\todo{CM}{ISO refs}], manuals [\todo{CM}{hedden book, skosify ref 3}], and scholarly articles [\todo{cm}{e.g., skosify refs 16/17}].
% TODO: bitte hier einfach nur die referenzen auf die wir uns beziehen zusammenfassen und kategorisieren. Schau dir dazu auch nochmals die SKOSify referenzen und die aus eurem iSemantics paper an.
If we want check existing SKOS vocabularies against these criteria, we first need to identify them and determine how to evaluate them given the syntax, structure and semantics of SKOS. Since we want to provide tool support for quality checking, we must formalize these criteria into computable metrics, in order to ensure consistent implementation and interpretation across tools.

### 2012-03-20 main.tex
minor consistency fixes in secs 1-3

The Simple Knowledge Organization System (SKOS) has become the standard model for expressing and publishing controlled vocabularies on the Web. However, SKOS vocabularies are often heterogeneous in terms of quality, which reduces their applicability across system boundaries. Here we investigate how we can support taxonomists in judging the quality of SKOS vocabularies by quality criteria that go beyond the low-level data model integrity constraints defined in the SKOS specification. Based on existing guidelines and best practices for creating controlled vocabularies, we identified existing \textbf{quality criteria}, formalized them into computable \textbf{filtering functions} that identify  affected resources and implemented them in the qSKOS quality assessment tool. We used that tool to analyze existing vocabularies and found that \todo{CM,BH}{summarize results in one sentence}.

>>>>

The Simple Knowledge Organization System (SKOS) has become a standard model for controlled Web vocabularies. However, SKOS vocabularies are often heterogeneous in terms of quality, which reduces their applicability across system boundaries. Here we investigate how we can support taxonomists in judging the quality of SKOS vocabularies by quality criteria that go beyond the low-level data model integrity constraints defined in the SKOS specification. We identified existing \textbf{quality criteria}, formalized them into computable \textbf{quality checking functions} that identify affected resources in a given SKOS vocabulary. We implemented these functions in the qSKOS quality assessment tool, analyzed \todo{CM}{XX} existing vocabularies and found possible quality issues in \todo{CM}{YY} vocabularies.
